%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Template for lab reports used at STIMA
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Sets the document class for the document
% Openany is added to remove the book style of starting every new chapter on an odd page (not needed for reports)
\documentclass[11pt, english, openany]{report}

%% Loading packages that alter the style
\usepackage[]{graphicx}
\usepackage[]{color}
\usepackage{alltt}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{color}
\usepackage[toc,page]{appendix}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{verbatim}
\usepackage{hyperref}
\hypersetup{
    colorlinks=blue,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\usepackage{listings}
\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{frame=tb,
   language=C++,
   aboveskip=3mm,
   belowskip=3mm,
   showstringspaces=false,
   columns=flexible,
   basicstyle={\small\ttfamily},
   numbers=none,
   numberstyle=\tiny\color{gray},
   keywordstyle=\color{blue},
   commentstyle=\color{dkgreen},
   stringstyle=\color{mauve},
   breaklines=true,
   breakatwhitespace=true
   tabsize=3
   }



\makeatletter
\newcommand{\ssymbol}[1]{^{\@fnsymbol{#1}}}
\makeatother

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

\definecolor{Black}{rgb}{.0,.0,.0}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}

% Set page margins
\usepackage[top=100pt,bottom=100pt,left=68pt,right=66pt]{geometry}

% Package used for placeholder text
\usepackage{lipsum}

% Prevents LaTeX from filling out a page to the bottom
\raggedbottom

% add English language
\usepackage[english]{babel}

% All page numbers positioned at the bottom of the page
\usepackage{fancyhdr}
\fancyhf{}                          % clear all header and footers
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}  % remove the header rule
\pagestyle{fancy}

% Changes the style of chapter headings
\usepackage{titlesec}
\titleformat{\chapter}
{\normalfont\LARGE\bfseries}{\thechapter.}{1em}{}
% Change distance between chapter header and text
\titlespacing{\chapter}{0pt}{50pt}{2\baselineskip}

% Adds table captions above the table per default
\usepackage{float}
\floatstyle{plaintop}
\restylefloat{table}

% Adds space between caption and table
\usepackage[tableposition=top]{caption}

% Adds hyperlinks to references and ToC
\usepackage{hyperref}
\hypersetup{hidelinks, linkcolor = blue} % Changes the link color to black and hides the hideous red border that usually is created

% If multiple images are to be added, a folder (path) with all the images can be added here
\graphicspath{ {images/} }

% Separates the first part of the report/thesis in Roman numerals
%\frontmatter

%% USER Package
\usepackage{tabularx}
\usepackage{titling}

%% title2.tex
\title{Course Report of \\ Operational Research 2}
\author{Luca Perali 1237770 \\ Michele Thiella 1206603}
\date{\today}

%% Starts the document
\begin{document}

	%% Selects the language to be used for the first couple of pages
	\selectlanguage{english}

	%% Adds the title page
	\input{title.tex}
	\input{abstract.tex}

	% Adds a table of contents
	\tableofcontents{}
	\clearpage

	%%%%
	%% The rows above should not be changed except for the title page information
	%%%% Text body starts here!
	%\mainmatter
	\input{model_description.tex}
	\input{CPLEX.tex}
	\input{meta-euristici.tex}
	\input{constructive-heuristics.tex}
	\input{refining-heuristics.tex}
	\input{repair.tex}
	\input{mip-heuristics.tex}
	\input{conclusion.tex}
	\clearpage
	
	\begin{appendices}
		\chapter{Test-bed} \label{sec:testset}
		The TSPLIB \cite{TSPLIB} is a library that contain different instances of TSP problem and its best solution found. All the file described in this section are part of the TSPLIB. To test the developed algorithm three different set have been prepared, depending on the number of node ($|V|$) in the graph: Data Light, Data Average and Data Heavy.\\
		These are all intended as sTSP, however the same instance can be considered also for aTSP replacing each edge with two arches with opposite direction. This subdivision is justified by the different execution time of the algorithms: it is more interesting to compare the performance of different algorithms in similar instances.
		
		\textbf{Data Light ($ |V| \le 150 $):}
		\begin{multicols}{5}
			att48.tsp \\
			berlin52.tsp \\
			bier127.tsp \\
			burma14.tsp \\
			ch130.tsp \\
			ch150.tsp \\
			eil101.tsp \\
			eil51.tsp \\
			eil76.tsp \\
			gr137.tsp \\
			gr96.tsp \\
			kroA100.tsp \\
			kroA150.tsp \\
			kroB100.tsp \\
			kroB150.tsp \\
			kroC100.tsp \\
			kroD100.tsp \\
			kroE100.tsp \\
			lin105.tsp \\
			pr107.tsp \\
			pr124.tsp \\
			pr136.tsp \\
			pr144.tsp \\
			pr76.tsp \\
			rat99.tsp \\
			rd100.tsp \\
			st70.tsp \\
			ulysses16.tsp \\
			ulysses22.tsp \\
		\end{multicols}
		\textbf{Data Average ($ 150 < |V| \le 300 $):}
		\begin{multicols}{5}
				a280.tsp \\
				d198.tsp \\
				gil262.tsp \\
				gr202.tsp \\
				gr229.tsp \\
				kroA200.tsp \\
				kroB200.tsp \\
				pr152.tsp \\
				pr226.tsp \\
				pr264.tsp \\
				pr299.tsp \\
				rat195.tsp \\
				rkoA200.tsp \\
				ts225.tsp \\
				tsp225.tsp \\
				u159.tsp \\
		\end{multicols}
		\textbf{Data Heavy ($|V| > 300$):}
		\begin{multicols}{5}
			ali535.tsp \\
			att532.tsp \\
			brd14051.tsp \\
			d1291.tsp \\
			d1655.tsp \\
			d18512.tsp \\
			d2103.tsp \\
			d493.tsp \\
			d657.tsp \\
			fl1400.tsp \\
			fl1577.tsp \\
			fl3795.tsp \\
			fl417.tsp \\
			fnl4461.tsp \\
			gr431.tsp \\
			gr666.tsp \\
			nrw1379.tsp \\
			p654.tsp \\
			pcb1173.tsp \\
			pcb3038.tsp \\
			pcb442.tsp \\
			pr1002.tsp \\
			pr2392.tsp \\
			pr439.tsp \\
			rat575.tsp \\
			rat783.tsp \\
			rd400.tsp \\
			rl11849.tsp \\
			rl1304.tsp \\
			rl1323.tsp \\
			rl1889.tsp \\
			rl5915.tsp \\
			rl5934.tsp \\
			u1060.tsp \\
			u1432.tsp \\
			u1817.tsp \\
			u2152.tsp \\
			u2319.tsp \\
			u574.tsp \\
			u724.tsp \\
			usa13509.tsp \\
			vm1084.tsp \\
			vm1748.tsp
		\end{multicols}
		
		\chapter{Performance measure} \label{sec:performance_meausure}
			In this chapter is discussed how the different deveeloped algorithms have been compared between each other.\\
			\textbf{Performance profile.} Exact algorithm (e.g. Subtour, MTZ and FC) guarantee to return the least expensive tour if would run for enough time, therefore a metric of interest is the total execution time needed to find the optimum. 
			Due to practical limitation, a time limit must be imposed. The performance profile compare for each tested instance ($ i $), the ratio ($ r^A(i) = \frac{t_{exec}^A(i)}{t_{exec}^*(i)} $) of the execution time of the algorithm A ($ t_{exec}^A(i) $) divided by the execution time of the faster algorithm ($ t_{exec}^*(i) $), for each $ k = 1, 2, .., K $ calculate the percentage expressed in fraction ($ \% $) of how many instances the algorithm A has $ r^A(i) \le k $ and the resultant function is the performance profile.
			The algorithm with the higher curve is the one who have been for more instances near the best.\\
			A problem of the performance profile is that some instances require fractions of second to be executed and little overhead would significantly influence the performance profile, however the purpose of this report is to measure the instance computability. For example if the faster algorithm run in 0.1s and A in 1s, $ r^A(i_1) = 10 $, which, for the performance profile, would be comparable to a second case where $ t_{exec}^*(i_2) = 100 $s and $ t_{exec}^A(i_2) = 1000 $s. To enhance the weight of the second cases, the calculated ratio is modified as follow: $ r^A(i) = \frac{t_{exec}^A(i)+T_{min}}{t_{exec}^*(i)+T_{min}} $. In this way, considering a $ T_{min} = 10$s, the $ r^A(i_1) = \frac{11.0}{10.1} = 1.08 $ and $ r^A(i_2) = \frac{1010.0}{110.} = 9.18 $ as desired.\\
			The second problem is for the instance that require a time near the time limit ($ T_{max} $). As an example, with $ T_{max} = 600 $s, if $ t_{exec}^*(i_1) = 590$s, two algorithm A and B without time limit would run for resp $ t_{exec}^A(i_1) = 601$s and $ t_{exec}^B(i_1) = 1200$s they would be comparable. Due to it is not possible to know how many time an algorithm would exceed the time limit, and in the same time it would be nice to "reward" the best algorithm, when $ t_{exec}^*(i) < T_{max} $ and $ t_{exec}^A(i) >= T_{max} $ the ratio is modified as:  $ r^A(i) = \frac{t_{exec}^A(i)R}{t_{exec}^*(i)} $ where $ R = $ "random value between $ \{1,..,k\} $". In this case, for a large number of case discussed above, the performance profile would not be modified. However it is known that for little number of instances, the performance profile is randomized therefore the result is useless and a warning message should be shown to avoid false considerations.
			
			\textbf{Random seed.} Due to some randomization is part of the proposed algorithm, it is possible to set the random seed generator. This is very useful either for reproduce a results or to avoid the \textit{performance variability} (PV). PV is intended here as an unwanted effect such that for infinitesimal change in the input (such as the random seed, the node order, etc.), there is a measurable change in the output. To avoid PV effect, as proposed in the course lesson, each algorithms is executed for each random seeds in a fixed set and the mean of the execution times is reported. Note that to calculate the execution times a random seed set of five integer has been used.
			
			\textbf{The number of threads.} The number of threads used is reported when necessary, otherwise the default value is used (4).
			
			\textbf{Machine architecture.} The machine used to run the algorithm and test the performance are two with two different OS and specific details are reported in tab \ref{tab:machines}.
			\begin{table}[h]
				\begin{center}
					\caption{Description of the machine used to run the algorithm and calculate the performance.}
					\label{tab:machines}
					\begin{tabular}{lll}
									&   \multicolumn{2}{c}{Machine ID} 	\\
						 			& L 				&	 M 			\\ \hline \\
						OS 			& Ubuntu 18.04LTS 	& Windows 10 	\\
						Processor	& Intel i7 8th Gen	&	Intel i5 9th Gen		\\
					\end{tabular}
				\end{center}
			\end{table}

		\chapter{CGAL Library in Windows with VS2019} \label{sec:cagalOne}
CGAL is a library that reliably simplifies access to computational geometry algorithms. It is written in C++ and therefore using the code:
\begin{lstlisting}
extern "C" {...}
\end{lstlisting}

it is possible to invoke C++ methods from a C file because it makes a function-name in C++ have C linkage. \\
Here are the steps to follow to use the CGAL library in a Windows environment with the IDE Visual Studio 2019 version.\\

\subsection{GMP in Windows} \label{sec:cgalLib}
First of all CGAL library use GMP, a free library arbitrary-precision arithmetic.  Unfortunately, it is not available for Windows, therefore is necessary to install these library: 
\begin{itemize}
	\item MPIR: a fork of GMP
	\item MPFR
	\item all boost library header files
\end{itemize}
Furthermore, the possibility of compiling the library is also explained.

\begin{itemize}
\item Follow steps at: \href{https://doc.cgal.org/latest/Manual/windows.html}{https://doc.cgal.org/latest/Manual/windows.html}. For the x64 version of CGAL, instead of command:
\begin{lstlisting}
./vcpkg.exe install cgal
\end{lstlisting}
 use next command:
\begin{lstlisting}
./vcpkg.exe install cgal:x64-windows   
\end{lstlisting}
\item (Not necessary) If you want to compile library use CygWin follow this guide: \\ \href{https://stackoverflow.com/questions/4711315/build-gmp-on-64bit-windows/52102540#52102540}{https://stackoverflow.com/questions/4711315/build-gmp-on-64bit-windows/52102540\#52102540} but replace command:
\begin{lstlisting}
./config --disable-static --enable-shared
\end{lstlisting}
with
\begin{lstlisting}
./configure --prefix=${gmp_build} --build=<config.guess output> --host=<config.guess output> --enable-cxx --with-gnu-ld --disable-static --enable-shared
\end{lstlisting}
where the \textit{<config.guess output>} is the output of command: 
\begin{lstlisting}
./config.guess
\end{lstlisting}
Now output file can be: DIR or DLL (respectively if used: \textit{--disable-static --enable-shared} OR \textit{--enable-static --disable-shared}).\\
Pay attention to the last command:
\begin{lstlisting}
 lib /machine:i386 /def:cyggmp-10.dll 
\end{lstlisting}
It must be run next to cyggmp-10.dll and the compiled library probably is located in Cygwin\textbackslash bin folder.
Lastly the option: \textit{/machine:i386} is for the 32bit version, \textit{/machine:x64} for the 64bit version. \\
\newline
Cygwin Package Information: To be more specific, in the tab.\ref{tab:packages} there are the packages and relative versions used to compile the CGAL library.
\begin{table}[h]
\scriptsize
	\begin{center}
		\caption{Output of command: \textit{cygcheck --check-setup} ran into Cygwin console which corresponds to the list of its installed packages and related versions.}
		\label{tab:packages}
		\begin{tabular}{ll|ll|ll}
			Package & Version & Package & Version & Package & Version \\ \hline
			&&&&& \\
			\_autorebase & 001007-1 & 	libdb5.3 & 5.3.28-2 & 	libsasl2\_3 & 2.1.27-1 \\
			alternatives & 1.3.30c-10 & 	libexpat1 & 2.2.6-1 & 	libsigsegv2 & 2.10-2 \\
			base-cygwin & 3.8-1 & 	libfdisk1 & 2.33.1-2 & 	libsmartcols1 & 2.33.1-2 \\
			base-files & 4.3-2 & 	libffi6 & 3.2.1-2 & 	libssh-common & 0.8.7-1 \\
			bash & 4.4.12-3 & 	libgc1 & 8.0.4-1 & 	libssh4 & 0.8.7-1 \\
			binutils & 2.34+1git.de9c1b7cfe-1 & 	libgcc1 & 9.3.0-2 & 	libssl1.1 & 1.1.1f-1 \\
			bzip2 & 1.0.8-1 & 	libgdbm4 & 1.13-1 & 	libstdc++6 & 9.3.0-2 \\
			ca-certificates & 2.40-1 & 	libgmp-devel & 6.2.0-2 & 	libtasn1\_6 & 4.14-1 \\
			cmake & 3.14.5-1 & 	libgmp10 & 6.2.0-2 & 	libunistring2 & 0.9.10-1 \\
			coreutils & 8.26-2 & 	libgmpxx4 & 6.2.0-2 & 	libuuid1 & 2.33.1-2 \\
			crypto-policies & 20190218-1 & 	libgomp1 & 9.3.0-2 & 	libuv1 & 1.32.0-1 \\
			cygutils & 1.4.16-2 & 	libgssapi\_krb5\_2 & 1.15.2-2 & 	libxml2 & 2.9.9-2 \\
			cygwin & 3.1.4-1 & 	libguile2.2\_1 & 2.2.7-1 & 	login & 1.13-1 \\
			cygwin-devel & 3.1.4-1 & 	libiconv & 1.14-3 & 	m4 & 1.4.18-1 \\
			dash & 0.5.9.1-1 & 	libiconv2 & 1.14-3 & 	make & 4.3-1 \\
			diffutils & 3.5-2 & 	libidn2\_0 & 2.2.0-1 & 	man-db & 2.7.6.1-1 \\
			editrights & 1.03-1 & 	libintl8 & 0.19.8.1-2 & 	mintty & 3.1.4-1 \\
			file & 5.32-1 & 	libisl22 & 0.22.1-2 & 	ncurses & 6.1-1.20190727 \\
			findutils & 4.6.0-1 & 	libjsoncpp19 & 1.8.4-1 & 	openssl & 1.1.1f-1 \\
			gawk & 5.1.0-1 & 	libk5crypto3 & 1.15.2-2 & 	p11-kit & 0.23.20-1 \\
			gcc-core & 9.3.0-2 & 	libkrb5\_3 & 1.15.2-2 & 	p11-kit-trust & 0.23.20-1 \\
			gcc-g++ & 9.3.0-2 & 	libkrb5support0 & 1.15.2-2 & 	pkg-config & 1.6.3-1 \\
			getent & 2.18.90-4 & 	libltdl7 & 2.4.6-7 & 	pkgconf & 1.6.3-1 \\
			grep & 3.0-2 & 	liblz4\_1 & 1.7.5-1 & 	publicsuffix-list-dafsa & 20200326-1 \\
			groff & 1.22.4-1 & 	liblzma5 & 5.2.4-1 & 	rebase & 4.4.4-1 \\
			gzip & 1.8-1 & 	libmpc3 & 1.1.0-1 & 	run & 1.3.4-2 \\
			hostname & 3.13-1 & 	libmpfr6 & 4.0.2-2p6 & 	sed & 4.4-1 \\
			info & 6.7-1 & 	libncursesw10 & 6.1-1.20190727 & 	tar & 1.29-1 \\
			ipc-utils & 1.0-2 & 	libnettle6 & 3.4.1-1 & 	terminfo & 6.1-1.20190727 \\
			less & 551-1 & 	libnghttp2\_14 & 1.37.0-1 & 	terminfo-extra & 6.1-1.20190727 \\
			libarchive13 & 3.3.2-1 & 	libopenldap2\_4\_2 & 2.4.49-1 & 	tzcode & 2019c-1 \\
			libargp & 20110921-3 & 	libp11-kit0 & 0.23.20-1 & 	tzdata & 2019c-1 \\
			libatomic1 & 9.3.0-2 & 	libpcre1 & 8.44-1 & 	util-linux & 2.33.1-2 \\
			libattr1 & 2.4.48-2 & 	libpipeline1 & 1.5.1-1 & 	vim-minimal & 8.2.0486-1 \\
			libblkid1 & 2.33.1-2 & 	libpkgconf3 & 1.6.3-1 & 	w32api-headers & 7.0.0-1 \\
			libbrotlicommon1 & 1.0.7-1 & 	libpopt-common & 1.16-2 & 	w32api-runtime & 7.0.0-1 \\
			libbrotlidec1 & 1.0.7-1 & 	libpopt0 & 1.16-2 & 	which & 2.20-2 \\
			libbz2\_1 & 1.0.8-1 & 	libpsl5 & 0.21.0-1 & 	windows-default-manifest & 6.4-1 \\
			libcom\_err2 & 1.44.5-1 & 	libquadmath0 & 9.3.0-2 & 	xz & 5.2.4-1 \\
			libcrypt2 & 4.4.4-1 & 	libreadline7 & 7.0.3-3 & 	zlib0 & 1.2.11-1 \\
			libcurl4 & 7.66.0-1 & 	librhash0 & 1.3.9-1 & 	\\

		\end{tabular}
	\end{center}
\end{table}
\end{itemize}

\subsection{Include GMP in Windows (if MPIR is not enough)}
MPIR is a highly optimised library for bignum arithmetic forked from the GMP bignum library. It is written in assembly language and C. It offers many features but in order to use the CGAL library correctly it is not enough, it is necessary to include GMP in the Visual Studio IDE.
\begin{enumerate}
\item \textit{VS} $\rightarrow$ \textit{Strumenti} $\rightarrow$ \textit{Gestione pacchetti NuGet} $\rightarrow$ \textit{Console di gestione pacchetti}:
	
\begin{lstlisting}
Install-Package NuGet.CommandLine
\end{lstlisting}	

\item \textit{VS} $\rightarrow$ \textit{Esplora Soluzione} $\rightarrow$ \textit{<nome\_progetto>} $\rightarrow$ \textit{packages.config} $\rightarrow$ add: 

\begin{lstlisting}
<package id="Baseclass.Contrib.Nuget.Output" version="2.4.3" targetFramework="native" />
<package id="Math.Gmp.Native.NET" version="2.0.6" targetFramework="native" />
<package id="NuGet.CommandLine" version="5.5.1" targetFramework="native" developmentDependency="true" />
\end{lstlisting}
		

\item Go on project folder (where \textit{<nome\_progetto>.sln} file is located, there should be "packages" folder) $\rightarrow$ open CMD :

\begin{lstlisting}
.\packages\NuGet.CommandLine.5.5.1\tools\NuGet.exe Install -NonInteractive -OutputDirectory packages packages.config
\end{lstlisting}
	
\item Close and reopen VS.

\item \textit{VS} $\rightarrow$ \textit{Esplora Soluzione} $\rightarrow$ \textit{<nome\_progetto>} $\rightarrow$ right click $\rightarrow$ \textit{Gestisci pacchetti NuGet}: \\
The 3 packages added in packages.config should be installed.\\
In top-right press the icon "settings" (near package origin). \\
In \textit{Gestione pacchetti NuGet} $\rightarrow$ \textit{Generale}: \\

	\textit{Cancella tutte le cache NuGet}

\item Close and reopen VS.
\end{enumerate}

Complete guide explained in \href{https://stackoverflow.com/a/33505176/2161332}{https://stackoverflow.com/a/33505176/2161332}. In our case, we didn't need to add the reference (from step 8 onwards).


\subsection{Add Library file}
\begin{enumerate}
\item \textit{VS} $\rightarrow$ \textit{Esplora Soluzione} $\rightarrow$ \textit{<nome\_progetto>} $\rightarrow$ right click $\rightarrow$ \textit{Proprietà}:

\item \textit{C/C++} $\rightarrow$ \textit{Generale} $\rightarrow$ \textit{Directory inclusioni aggiuntive} $\rightarrow$ \textit{add}:

\begin{lstlisting}
<local_path_to>\vcpkg\installed\x64-windows\include
<local_path_to>\vcpkg\packages\mpfr_x64-windows\bin
<local_path_to>\vcpkg\packages\mpir_x64-windows\bin
\end{lstlisting}
	
\item \textit{Linker} $\rightarrow$ \textit{Generale} $\rightarrow$ \textit{Directory librerie aggiuntive} $\rightarrow$ \textit{add}:

\begin{lstlisting}
<local_path_to>\vcpkg\installed\x64-windows\lib
\end{lstlisting}

	 $\rightarrow$ \textit{Input} $\rightarrow$ \textit{add}:
\begin{lstlisting}
mpfr.lib
mpir.lib	
\end{lstlisting}
\end{enumerate}
	
\subsection{Test CGAL (with GMP)}
Copy and paste in file.cpp and try to run:

\begin{lstlisting}
#include <iostream>
#include <CGAL/Exact_predicates_inexact_constructions_kernel.h>
#include <CGAL/convex_hull_2.h>

typedef CGAL::Exact_predicates_inexact_constructions_kernel K;
typedef K::Point_2 Point_2;
    
int main()
{
	Point_2 points[5] = { Point_2(0,0), Point_2(10,0), Point_2(10,10), Point_2(6,5), Point_2(4,1) };
	Point_2 result[5];
	Point_2* ptr = CGAL::convex_hull_2(points, points + 5, result);
	std::cout << ptr - result << " points on the convex hull:" << std::endl;
	for (int i = 0; i < ptr - result; i++) {
		std::cout << result[i] << std::endl;
	}
	return 0;
}
\end{lstlisting}

\subsection{Solution to Error Framework}
\begin{itemize}
\item \textit{VS} $\rightarrow$ \textit{Esplora Soluzione} $\rightarrow$ \textit{<nome\_progetto>} $\rightarrow$ right click $\rightarrow$ \textit{Gestisci pacchetti NuGet}: check the require .NET Framework
\end{itemize}
It can be possible to change used Framework directy on VS settings :
\begin{enumerate}
\item \textit{VS} $\rightarrow$ \textit{Esplora Soluzione} $\rightarrow$ \textit{<nome\_progetto>} $\rightarrow$ right click $\rightarrow$ \textit{Proprietà}:
\item \textit{Proprietà di configurazione} $\rightarrow$ \textit{Avanzate} $\rightarrow$ \textit{Versione di .NET Framework di destinazione}: insert .NET Framework version previously checked.
\end{enumerate}
(reference: \href{https://docs.microsoft.com/it-it/cpp/build/how-to-modify-the-target-framework-and-platform-toolset?view=vs-2019}{https://docs.microsoft.com/it-it/cpp/build/how-to-modify-the-target-framework-and-platform-toolset?view=vs-2019})
\begin{itemize}
\item then, close and restart VS
\end{itemize}

\subsection{Relative Links}
\href{https://www.cgal.org/download/windows.html}{https://www.cgal.org/download/windows.html}\\
\href{https://stackoverflow.com/questions/30181324/building-visual-c-applications-with-cgal-library}{https://stackoverflow.com/questions/30181324/building-visual-c-applications-with-cgal-library}\\
\href{https://stackoverflow.com/questions/4711315/build-gmp-on-64bit-windows}{https://stackoverflow.com/questions/4711315/build-gmp-on-64bit-windows}\\
\href{https://doc.cgal.org/latest/Manual/windows.html}{https://doc.cgal.org/latest/Manual/windows.html}\\
\href{https://stackoverflow.com/questions/17385988/getting-gmp-libraries-to}{https://stackoverflow.com/questions/17385988/getting-gmp-libraries-to}\\
\href{https://docs.microsoft.com/it-it/cpp/build/how-to-modify-the-target-framework-and-platform-toolset?view=vs-2019}{https://docs.microsoft.com/it-it/cpp/build/how-to-modify-the-target-framework-and-platform-toolset?view=vs-2019}\\
\href{https://stackoverflow.com/questions/18694947/how-can-i-make-my-managed-nuget-package-support-c-cli-projects}{https://stackoverflow.com/questions/18694947/how-can-i-make-my-managed-nuget-package-support-c-cli-projects}\\
(\href{https://docs.microsoft.com/it-it/visualstudio/ide/how-to-add-or-remove-references-by-using-the-reference-manager?view=vs-2019}{https://docs.microsoft.com/it-it/visualstudio/ide/how-to-add-or-remove-references-by-using-the-reference-manager?view=vs-2019})\\
	\end{appendices}
	

	% Adding a bibliography if citations are used in the report
	\bibliographystyle{plain}
	\bibliography{bibliography.bib}
	% Adds reference to the Bibliography in the ToC
	\addcontentsline{toc}{chapter}{\bibname}

\end{document}